Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-01-13 ms/S2_appendix.tex
worked on todo

>>>>

\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_4.pdf}
\caption{{\bf Effects of contact heterogeneity and vital dynamics.}
This figure matches Fig 3 in main text, but displays the
summary statistics of the modified explicit model (models with contact heterogeneity and vital dynamics).
Summary statistics of an each model is represented by shapes and all models were simulated using the baseline parameters.
}
\label{fig:fig3aug}
\end{figure}
